Figures

### 2021-06-02 figure.Rmd
edits: figure diversity

```{r, fig.height=6, fig.width=8, fig.cap="Influences of ecosystem size (A, watershed area) and complexity (B, branching probability) on $\\alpha$ (left), $\\beta$ (middle), and $\\gamma$ diversity (right) in Hokkaido and Midwest regions. Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the robust regression models."}

>>>>

```{r, fig.height=7, fig.width=8, fig.cap="Influences of ecosystem size (A, watershed area) and complexity (B, branching probability) on $\\alpha$ (red), $\\beta$ (green), and $\\gamma$ diversity (blue) in Hokkaido and Midwest regions. Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the robust regression models."}
